\bf\mftitle

### 2011-03-02 doc/jInfer/basicxsd/basicxsd.tex
last minute corrections

The main class implementing \code{SchemaGenerator} inference interface and simultaneously registered as its service provi\-der is \code{SchemaGeneratorImpl} in package \code{cz.cuni.mff.ksi.jinfer.basicxsd}. Process of export consists of two phases described in detail in later sections.
\begin{enumerate}
	\item Preprocessing.
	\item The export to a string representation itself.
\end{enumerate}
Method \code{start()} first creates an instance of \code{Preprocessor} class supplying the rules (elements) it got in the simplified grammar on input. Preprocessing itself is done by creating that instance (calling its constructor) and its results can be then retrieved by calling \code{getResult()} method. Purpose of preprocessing is to discover information necessary for export of elements. For example, determine elements which should be globally defined or which element is the root element.\\

@@

If it is desired to not generate global types, this feature can be turned off in preferences. However, turning it off is not recommended and in some cases it may cause invalidity of resulting XSD output. For more information, see \ref{section:problems}.\\

Minimal number of occurrences of an element to define its type globally can be altered if preferences as well. See \ref{subsection:preferences}.

@@

To generate a human readable XSD output, it is necessary to apply correct indentation of XSD elements and their content. This is handled by \code{Indentator} class. This classes also serves as a buffer for string representation of XSD that the exporter is creating.\\

@@

Number of spaces characters per one level of indentation can be altered in project properties, see \ref{subsection:preferences}.

@@

Before we describe the export of elements, let's take a look on how we define elements and their attributes using XSD language. This subsection covers only XSD features that the exporter supports. For list of supported features, see \ref{subsection:supportedXSDFeatures}\\

@@

Classes to handle export of elements are in package \code{cz.cuni.mff.ksi.jinfer.basicxsd.elementsexporters}. Basic common logic is implemented in \code{AbstractElementsExporter} class. This class is abstract and is supposed to be extended by classes with a particular purpose. Its constructor signature is defined as following.

@@

Names of parameters are self explanatory. Parameter \code{preprocessingResult} is a result of preprocessing. Parameter \code{indentator} is an instance of \code{Indentator} class to be used to buffer and indent output of exporter. This instance doesn't need to be empty . Output of exporter is appended at the end of text held by the \code{indentator}. This behaviour is convenient when chaining output of several elements exporters.\\

@@

If a global type contains other elements, these are processed as following.

@@

This module is just basic implementation, thus many XSD features are not supported. List of supported XSD elements and their attributes follows. Let \code{xs} be XMLSchema namespace.

@@

This basic implementation of XSD export does not support and does not handle namespaces. That means that no namespace definitions are generated in a result, namespace definitions in input are processed as regular elements and attributes and namespace usages (namespace:element) are considered as a part of name of an element.

>>>>

The main class implementing \code{SchemaGenerator} inference interface and simultaneously being registered as its service provi\-der is \code{SchemaGeneratorImpl} in package \code{cz.cuni.mff.ksi.jinfer.basicxsd}. Process of export consists of two phases described in detail in later sections.
\begin{enumerate}
	\item Preprocessing.
	\item The export to a string representation itself.
\end{enumerate}
Method \code{start()} first creates an instance of \code{Preprocessor} class supplying the rules (elements) it got from the simplified grammar on input. Preprocessing itself is done by creating that instance (calling its constructor) and its results can be then retrieved by calling \code{getResult()} method. Purpose of preprocessing is to discover information necessary for export of elements. For example, determine elements which should be globally defined or which element is the root element.\\

@@

If it is desired to not generate global types, this feature can be turned off in preferences. However, turning it off is not recommended and in some cases it may cause invalidity of the resulting XSD output. For more information, see section \ref{section:problems}.\\

Minimal number of occurrences of an element to define its type globally can be altered if preferences as well. See subsection \ref{subsection:preferences}.

@@

To generate a human readable XSD output, it is necessary to apply correct indentation of XSD elements and their content. This is handled by \code{Indentator} class. This class also serves as a buffer for string representation of XSD that the exporter is creating.\\

@@

Number of spaces characters per one level of indentation can be altered in project properties, see paragraph \ref{subsection:preferences}.

@@

Before we describe the export of elements, let's take a look on how we define elements and their attributes using XSD language. This subsection covers only XSD features that the exporter supports. For list of supported features, please refer to section \ref{subsection:supportedXSDFeatures}\\

@@

Classes to handle export of elements are in package \code{cz.cuni.mff.ksi.jinfer.basicxsd.elementsexporters}. Basic common logic is implemented in \code{AbstractElementsExporter} class. This class is abstract and is supposed to be extended by classes with a particular purpose. Its constructor signature is defined as follows.

@@

Names of parameters are self explanatory. Parameter \code{preprocessingResult} is a result of preprocessing. Parameter \code{indentator} is an instance of \code{Indentator} class to be used to buffer and indent output of exporter. This instance doesn't need to be empty. Output of exporter is appended at the end of text held by the \code{indentator}. This behaviour is convenient when chaining output of several elements exporters.\\

@@

If a global type contains other elements, these are processed as follows.

@@

This module is just basic implementation, thus many XSD features are not supported. A list of supported XSD elements and their attributes follows. Let \code{xs} be XMLSchema namespace.

@@

This basic implementation of XSD export does not support, nor handle, namespaces; that means that no namespace definitions are generated in the result. Namespace definitions in input are processed as regular elements and attributes, and namespace usages (namespace:element) are considered as a part of the name of an element.
